**Machine learning identifies unique taxa differentiating proximal and distal

### 2017-06-06 submission/manuscript.Rmd
working on the intro

Colorectal cancer (CRC) is the second-leading cause of cancer-related deaths in the United States (cite). CRC tumors vary in structure, size, morbidity and symptomology depending upon their geographical location in the colon. Tumors found in the proximal colon are typically flatter, sessile tumors that form along the inside of the colon wall whereas tumors of the distal colon are bulbous and project into the lumen. These features make cancers of the proximal colon less likely to present with bowel symptoms and thus are associated with an increase in morbidity and mortality (cite).

The human colon contains a number of microhabitats that enrich for different microbial membership at each site. Indeed, a number of studies have demonstrated that microbial populations differ throughout the gastrointestinal tract.

>>>>

Colorectal cancer (CRC) is the second-leading cause of cancer-related deaths in the United States (cite). CRC tumors vary in structure, size, morbidity and symptomology depending upon their geographical location in the colon. Tumors found in the proximal colon are typically flatter, sessile tumors that form along the inside of the colon wall whereas tumors of the distal colon are bulbous and project into the lumen. These features make cancers of the proximal colon less likely to present with bowel symptoms and thus are associated with an increase in morbidity and mortality (cite). The proximal and distal human colon are comprised of different microhabitats that likely enrich for different microbial membership at each site. Indeed, a number of studies have demonstrated that microbial populations differ throughout the gastrointestinal tract in accordance with oxygen, nutrient and pH gradients (cite). Further, our group and others have found that the stool microbiome of patients with CRC is distinct from that of healthy people (cite).

These studies have been limited though by the sample collection methods. Nearly all human gut microbiome studies have been performed on whole shed stool or on samples collected during colonoscopy procedures (cite). While the latter method allows investigators to acquire samples from inside the human colon, typically this procedure is preceded by the use of bowel preparation methods such as the consumption of laxatives to cleanse the bowel (cite). Bowel preparation is essential for detecting cancerous or precancerous lesions in the colon, but has been proven to disrupt the normal gut microbiome
